### 2018-12-04 dissertation.tex
maybe final version

% DATE OF SUBMISSION
May 2018
\end{center}	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In the third essay, I employ extreme bounds analysis and distributed random forests to identify the key determinants of state-sponsored violence. Although the literature on mass killings has grown significantly over the last decades, it remains unclear whether estimates are robust to different model specifications or which variables accurately predict the onset of genocides and politicides. To address these issues, I test the sensitivity of 40 variables on a sample of 177 countries from 1945 to 2013. The results show that GDP per capita, the post-Cold War period, and stable political regimes are negatively associated with mass killings. In contrast, ethnic diversity, civil wars, and previous political turmoils increase the risk of state-led violence. Mass killings that occur during civil wars are correlated with a different set of covariates, and I find that territorial conflicts and the use of militias are negatively associated with the outcome variable. The random forests estimations indicate that years since the last episode of mass violence, GDP per capita, urban population, ethnic polarisation, the number of military personnel, and democracy make the greatest contribution to the models' out-of-sample predictive power.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% DATE OF SUBMISSION
December 2018
\end{center}	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In the third essay, I employ extreme bounds analysis and distributed random forests to identify the key determinants of state-sponsored violence. Although scholars have suggested a number of potential correlates of mass killings, it remains unclear whether the estimates are robust to different model specifications, or which variables accurately predict the onset of large-scale violence. I employ extreme bounds analysis and random forests to test the sensitivity of 40 variables on a sample of 177 countries from 1945 to 2013. The results help clear the brush around mass killings, as few variables in this literature are robust determinants of atrocity. However, support for an opportunity logic persists as greater constraints on a government limit its ability to employ barbarous tactics. It appears that the Conflict Trap applies to government atrocity. Atrocity breeds atrocity, while wealthy stable democracies tend to avoid episodes of mass killing.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
